### 2017-10-18 Risk analysis/Text/Layout/Layout/chapter3_results.tex
inserted things to not forget in results section

				In this first case, a normal distribution with a mean of 25~m and a standard deviation of 20~m is chosen to reflect the likelihood of the seal thickness. For the reservoir, a normal distribution with a mean of 180~m and a standard deviation of 60~m is chosen. Using these likelihoods to update the 1D geological model, the uncertainty in the posterior probability distributions for the positions of layer boundaries in depth is reduced (see Figure \ref{fig:update_moderate1}).\\					
				Scoring is applied based on these new distributions. In Figure \ref{fig:update_moderate2_3}-A, it can be recognized that the bulk of the score distribution was shifted to the positive side of values, while the peak at -2000 was raised. The probability of scores between -2000 and 0 decreased significantly, i.e. the true score is most likely either positive or -2000 if it is negative.\\
				Application of the custom loss function (Equation \ref{eq:LFR_final}) is visualized in Figure \ref{fig:update_moderate2_3}, in which the expected losses are compared before (B1) and after (B2) uncertainty reduction. It is observable, that by adding information about layer thickness likelihoods, Bayes actions are shifted relative to the nature of the information. In this case, the added data generally reinforces the probability of the reservoir to be significantly thick. Information on the seal, however, based on a normal distribution around 25~m thickness, leaves uncertainty about the reliability of the seal, as the safety threshold is defined as 20~m.\\				
				Increased certainty about the reservoir thickness is sufficient to shift Bayes actions to higher estimates for all actors, but the most risk-averse one ($r$ = 1.5). These shifts are quantified in Table \ref{tab:update_examples_all}. According to these numbers, the risk-neutral actor's estimate is increased the most, the risk-friendliest actor's estimate the least. Expected losses are decreased for the risk-neutral and the two risk-friendlier individuals. It is clear that the expected loss was reduced the most for the risk-friendliest actor and it increased most significantly for the most risk-averse actor.\\				
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & +~553.67 & -~105.49 \\ 
				%		0.75 & +~673.40 & -~81.67  \\ 
				%		1.00 & +~750.05 & -~33.56 \\ 
				%		1.25 & +~713.19 & +~75.71 \\ 
				%		1.50 & +~0.00 & +~282.64  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_moderate_tab}
				%\end{table}

				\subsubsection{Updating case II: Likely reliable seal}
				\begin{figure}[h]
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_goodseal2.png}
						%\caption{1a}
						%\label{fig:sfig1}
					\end{subfigure}%
					\\
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_goodseal3.png}
						%\caption{1b}
						%\label{fig:sfig2}
					\end{subfigure}
					\caption{Reservoir score distributions (A) and change in the realizations of expected loss for several risk parameters (B1, B2) before and after Bayesian updating based on likelihoods defined as follows: Seal thickness mean = 50~m, std = 20~m. Reservoir thickness mean = 180~m, std = 60~m.}
					\label{fig:update_goodseal2_3}
				\end{figure}
				In this second case, the reservoir thickness likelihood is defined in the same way as in case I (mean = 180~m, standard deviation = 60~m). For the seal, a mean of 50~m with a standard deviation of 20~m is chosen, favoring the likelihood of a reliable seal relative to the threshold of 20~m thickness. Respective score results are depicted in Figure \ref{fig:update_goodseal2_3}-A. The bulk of the distribution is narrowed on the positive side of estimates. Mean and median are clearly shifted to higher values. The "seal failure peak" at -2000 is significantly decreased.\\		
				Applying the custom loss function on this new score distribution results in the realizations of expected loss illustrated in Figure \ref{fig:update_goodseal2_3}. Bayes actions are shifted clearly to higher estimates and expected losses of these minima are significantly reduced for all actors. This is quantified in Table \ref{tab:update_examples_all}. According to these values, the risk-neutral to risk-averse individuals seem to profit the most, due to a large change in estimate value and decreased expected loss. Compared to case I, the estimate shifts for both risk-friendlier actors remain approximately the same, expected losses, however, are lowered much more significantly.\\		
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & +~522.95 & -~436.26 \\ 
				%		0.75 & +~697.73 & -~551.92  \\ 
				%		1.00 & +~855.57 & -~631.92 \\ 
				%		1.25 & +~912.43 & -~647.10 \\ 
				%		1.50 & +~819.26 & -~545.96  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_goodseal_tab}
				%\end{table}

				\subsubsection{Updating case III: Safe seal but likely subpar reservoir thickness}
				\begin{figure}[h]
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_smallres2.png}
						%\caption{1a}
						%\label{fig:sfig1}
					\end{subfigure}%
					\\
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_smallres3.png}
						%\caption{1b}
						%\label{fig:sfig2}
					\end{subfigure}
					\caption{Reservoir score distributions (A) and change in the realizations of expected loss for several risk parameters (B1, B2) before and after Bayesian updating based on likelihoods defined as follows: Seal thickness mean = 70~m, std = 10~m. Reservoir thickness mean = 100~m, std = 40~m.}
					\label{fig:update_smallres2_3}
				\end{figure}
				In this third case, seal safety is ensured by using a mean of 70~m with a standard deviation of 10~m for the seal thickness likelihood. However, the new observations are assumed to provide information about the reservoir unit that makes it likely to be thinner than expected. Reservoir thickness likelihood is assigned a mean of 100~m and a standard deviation of 40~m.\\				
				The subsequent score distribution is depicted in Figure \ref{fig:update_smallres2_3}. It can be seen that while the whole distribution is narrowed, it also is shifted to the left, to lower and negative estimates. Mean and median are almost the same. As seal reliability is practically guaranteed, the peak at -2000~m vanishes.\\				
				Based on this reservoir score probability distribution, Bayes actions are shifted to lower estimates for all actors using the custom loss function (see Figure \ref{fig:update_smallres2_3}). In fact, all but the most risk-friendly individual (\textit{r}~=~0.5) find their Bayesian estimator to be zero now, i.e. project development is deemed to be too risky to them. Furthermore, the spread of expected loss values around the minima for all actors is diminished. In other words, the expected loss values of the Bayes actions are now much closer to each other. Notable is the large reduction of expected loss in general. Quantified changes in the positions and values of the Bayes actions are listed in Table \ref{tab:update_examples_all}. There is no shift in estimate for risk-averse actors, as they already found their best estimates to be zero before updating.\\
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & -~498.98 & -~538.08 \\ 
				%		0.75 & -~346.16 & -~717.83  \\ 
				%		1.00 & -~176.13 & -~872.02 \\ 
				%		1.25 & -~0.00 & -~946.04 \\ 
				%		1.50 & -~0.00 & -~951.57  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_smallres_tab}
				%\end{table}

>>>>

				In this first case, a normal distribution with a mean of 25~m and a standard deviation of 20~m is chosen to reflect the likelihood of the seal thickness. For the reservoir, a normal distribution with a mean of 180~m and a standard deviation of 60~m is chosen. Using these likelihoods to update the 1D geological model, the uncertainty in the posterior probability distributions for the positions of layer boundaries in depth is reduced (see Figure \ref{fig:update_moderate1}).\\					
				Scoring is applied based on these new distributions. In Figure \ref{fig:update_moderate2_3}-A, it can be recognized that the bulk of the score distribution was shifted to the positive side of values, while the peak at -2000 was raised. The probability of scores between -2000 and 0 decreased significantly, i.e. the true score is most likely either positive or -2000 if it is negative.\\
				Application of the custom loss function (Equation \ref{eq:LFR_final}) is visualized in Figure \ref{fig:update_moderate2_3}, in which the expected losses are compared before (B1) and after (B2) uncertainty reduction. It is observable, that by adding information about layer thickness likelihoods, Bayes actions are shifted relative to the nature of the information. In this case, the added data generally reinforces the probability of the reservoir to be significantly thick. Information on the seal, however, based on a normal distribution around 25~m thickness, leaves uncertainty about the reliability of the seal, as the safety threshold is defined as 20~m.\\				
				NOT INCREASED CERTAINTY; ONLY OVERALL VALUES!
				Increased certainty about the reservoir thickness is sufficient to shift Bayes actions to higher estimates for all actors, but the most risk-averse one ($r$ = 1.5). These shifts are quantified in Table \ref{tab:update_examples_all}. According to these numbers, the risk-neutral actor's estimate is increased the most, the risk-friendliest actor's estimate the least. Expected losses are decreased for the risk-neutral and the two risk-friendlier individuals. It is clear that the expected loss was reduced the most for the risk-friendliest actor and it increased most significantly for the most risk-averse actor.\\				
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & +~553.67 & -~105.49 \\ 
				%		0.75 & +~673.40 & -~81.67  \\ 
				%		1.00 & +~750.05 & -~33.56 \\ 
				%		1.25 & +~713.19 & +~75.71 \\ 
				%		1.50 & +~0.00 & +~282.64  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_moderate_tab}
				%\end{table}

				\subsubsection{Updating case II: Likely reliable seal}
				\begin{figure}[h]
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_goodseal2.png}
						%\caption{1a}
						%\label{fig:sfig1}
					\end{subfigure}%
					\\
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_goodseal3.png}
						%\caption{1b}
						%\label{fig:sfig2}
					\end{subfigure}
					\caption{Reservoir score distributions (A) and change in the realizations of expected loss for several risk parameters (B1, B2) before and after Bayesian updating based on likelihoods defined as follows: Seal thickness mean = 50~m, std = 20~m. Reservoir thickness mean = 180~m, std = 60~m.}
					\label{fig:update_goodseal2_3}
				\end{figure}
				In this second case, the reservoir thickness likelihood is defined in the same way as in case I (mean = 180~m, standard deviation = 60~m). For the seal, a mean of 50~m with a standard deviation of 20~m is chosen, favoring the likelihood of a reliable seal relative to the threshold of 20~m thickness. Respective score results are depicted in Figure \ref{fig:update_goodseal2_3}-A. The bulk of the distribution is narrowed on the positive side of estimates. Mean and median are clearly shifted to higher values. The "seal failure peak" at -2000 is significantly decreased.\\		
				Applying the custom loss function on this new score distribution results in the realizations of expected loss illustrated in Figure \ref{fig:update_goodseal2_3}. Bayes actions are shifted clearly to higher estimates and expected losses of these minima are significantly reduced for all actors. This is quantified in Table \ref{tab:update_examples_all}. According to these values, the risk-neutral to risk-averse individuals seem to profit the most, due to a large change in estimate value and decreased expected loss. Compared to case I, the estimate shifts for both risk-friendlier actors remain approximately the same, expected losses, however, are lowered much more significantly.
				POINT OUT: DECREASED UNCERTAINTY! AND HIGHER VALUES OVERALL!\\		
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & +~522.95 & -~436.26 \\ 
				%		0.75 & +~697.73 & -~551.92  \\ 
				%		1.00 & +~855.57 & -~631.92 \\ 
				%		1.25 & +~912.43 & -~647.10 \\ 
				%		1.50 & +~819.26 & -~545.96  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_goodseal_tab}
				%\end{table}

				\subsubsection{Updating case III: Safe seal but likely subpar reservoir thickness}
				\begin{figure}[h]
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_smallres2.png}
						%\caption{1a}
						%\label{fig:sfig1}
					\end{subfigure}%
					\\
					\begin{subfigure}{1\textwidth}
						\centering
						\includegraphics[width=1\linewidth]{Figures/update_smallres3.png}
						%\caption{1b}
						%\label{fig:sfig2}
					\end{subfigure}
					\caption{Reservoir score distributions (A) and change in the realizations of expected loss for several risk parameters (B1, B2) before and after Bayesian updating based on likelihoods defined as follows: Seal thickness mean = 70~m, std = 10~m. Reservoir thickness mean = 100~m, std = 40~m.}
					\label{fig:update_smallres2_3}
				\end{figure}
				In this third case, seal safety is ensured by using a mean of 70~m with a standard deviation of 10~m for the seal thickness likelihood. However, the new observations are assumed to provide information about the reservoir unit that makes it likely to be thinner than expected. Reservoir thickness likelihood is assigned a mean of 100~m and a standard deviation of 40~m.\\				
				The subsequent score distribution is depicted in Figure \ref{fig:update_smallres2_3}. It can be seen that while the whole distribution is narrowed, it also is shifted to the left, to lower and negative estimates. Mean and median are almost the same. As seal reliability is practically guaranteed, the peak at -2000~m vanishes.\\				
				Based on this reservoir score probability distribution, Bayes actions are shifted to lower estimates for all actors using the custom loss function (see Figure \ref{fig:update_smallres2_3}). In fact, all but the most risk-friendly individual (\textit{r}~=~0.5) find their Bayesian estimator to be zero now, i.e. project development is deemed to be too risky to them. Furthermore, the spread of expected loss values around the minima for all actors is diminished. In other words, the expected loss values of the Bayes actions are now much closer to each other. Notable is the large reduction of expected loss in general. Quantified changes in the positions and values of the Bayes actions are listed in Table \ref{tab:update_examples_all}. There is no shift in estimate for risk-averse actors, as they already found their best estimates to be zero before updating.
				DECREASED UNCERTAINTY BUT AT THE SAME TIME LOWER VALUES OVERALL!\\
				%\begin{table}
				%	\centering
				%	\begin{tabular}[c]{| l | l | l |}
				%		\hline
				%		Risk factor \textit{r} & Shift in Bayes action & Change in expected loss \\ \hline
				%		0.50 & -~498.98 & -~538.08 \\ 
				%		0.75 & -~346.16 & -~717.83  \\ 
				%		1.00 & -~176.13 & -~872.02 \\ 
				%		1.25 & -~0.00 & -~946.04 \\ 
				%		1.50 & -~0.00 & -~951.57  \\ 
				%		\hline
				%	\end{tabular}
				%	\caption{Bla}
				%	\label{tab:update_smallres_tab}
				%\end{table}
